\Large\textbf{Decentralized Data Marketplace to Enable Trusted Machine Economy}

### 2019-10-22 paper.tex
Cite GDPR paper for TangleID

Looking at Airbox\cite{LASS} as an example, every household with an Airbox device can collect air quality records automatically and autonomically—rather than passively receive the outcomes from the centralized authorities. To protect privacy, data should be encrypted before going on-chain. As for data reliability, we extended the backbone design of the Airbox to interoperate smart-contract-oriented structure to record every transaction. At the same time, data on-chain will send a verifiable request to mark itself as "being tradeable." This step enables buyers to review and bargain at will. Last but not least, payments will be stored on the smart contracts until the transactions are confirmed. The entire sequence is illustrated in Figure \ref{fig:airbox}.

\begin{figure}[h]
    \centering
    \includegraphics[width=0.5\textwidth]{airbox}
    \caption{IoT-enabled personal air quality assistant.}
    \label{fig:airbox}
\end{figure}

@@

Figure.\ref{fig:decision_tree} shows the decision tree to depict the repeated game we used. Each level in this decision tree represents each round of data transmission from data provider to consumers, and the consumers would pay subscription fee, $p_s$, for each person. The sum of all the subscription fee paid to the data provider is denoted as $P_s$.

\begin{figure} \centering \includegraphics[width=3.3in]{decision_tree} \caption{Decision Tree}
    \label{fig:decision_tree} \end{figure}
For every $n$ round, the data provider would pay $C_{maintain}$ to enhance the sensors that the data provider owns. We call this a maintenance period. Moreover, the value of data and the cost of maintenance will decrease as time passes, so we introduce a discounted factor $\beta$ to depict this phenomena.

@@

Substitute Eq. (\ref{sub_fee}) and Eq. (\ref{C_mtn}) into Eq. (\ref{payoff}). We can derive
\begin{equation} \label{payoff_Pr}
    \sum_{i=0}^{m - 1}{\beta^{in}\cdot [(\sum_{j=0}^{n - 1} \beta^j \cdot R \frac{e^{a (P_r - b)}}{1 + e^{a (P_r - b)}}) - ce^{P_r - d}]}
\end{equation}

Let tuning factors $, a = 0.15, b = 50, R = 10000, c = 1, d = 88$, and only one maintenance period has occured and one maintenance period consists of 12 rounds which means $m = 1, n = 12$. Based on these parameters, we can plot the payoff function as a function of accuracy, $Pr$ which is Figure.\ref{fig:payoff_pic}. The maximum point occurs at $accuracy \approx 92\%$ which is indicated with a red dot.
\begin{figure} \centering \includegraphics[width=3.3in]{payoff_pic} \caption{Payoff Function}
    \label{fig:payoff_pic} \end{figure}

Figure.\ref{fig:payoff_pic} illustrates the market mechanism of the subscription trading policy we used under the decentralized data marketplace. First, data providers have weak motivation to operate their sensor in low accuracy, since the incentive of low quality data is much less than moderate quality data. Second the great deficit at high accuracy is mostly derived by the rapid increasing of maintenance cost. Thus, if the maintenance fee to achieve decent data quality is under a fair price range, then data provider will automatically provide data with high enough data quality under our assumptions.

>>>>

@@

Each consumer would pay subscription fee, $p_s$, each time they receive data from data provider. The sum of all the subscription fee paid to the data provider is denoted as $P_s$.

For every $n$ round, the data provider would pay $C_{maintain}$ to enhance the sensors that the data provider owns. We call this a maintenance period. Moreover, the value of data and the cost of maintenance will decrease as time passes, so we introduce a discounted factor $\beta$ to depict this phenomena.

@@

Substitute Eq. (\ref{sub_fee}) and Eq. (\ref{C_mtn}) into Eq. (\ref{payoff}). We can derive an equation illustrating the market mechanism of the subscription trading policy we used under the decentralized data marketplace. First, data providers have weak motivation to operate their sensor in low accuracy, since the incentive of low quality data is much less than moderate quality data. Second the great deficit at high accuracy is mostly derived by the rapid increasing of maintenance cost. Thus, if the maintenance fee to achieve decent data quality is under a fair price range, then data provider will automatically provide data with high enough data quality under our assumptions.
